Hourly Assimilation of Different Sources of Observations Including Satellite Radiances in a Mesoscale Convective System Case During RELAMPAGO campaign

### 2022-08-27 analysis/paper/paper_ana_20181122.tex

\documentclass[authoryear,preprint,review,12pt]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
\usepackage[hyphens]{url}

@@

\usepackage{lineno} % add

@@

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{graphicx}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Hourly Assimilation of Different Sources of Observations Including Satellite Radiances in a Mesoscale Convective System Case During RELAMPAGO campaign},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

\usepackage{lineno}
\linenumbers
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

  \title{Hourly Assimilation of Different Sources of Observations Including Satellite Radiances in a Mesoscale Convective System Case During RELAMPAGO campaign}
    \author[UBA,CIMA,CNRS]{Paola Belén Corrales\corref{1}}
   \ead{paola.corrales@cima.fcen.uba.ar} 
    \author[UBA,CIMA,CNRS]{Victoria Galligani}

@@

      \address[UBA]{Universidad de Buenos Aires, Facultad de Ciencias Exactas y Naturales, Departamento de Ciencias de la Atmósfera y los Océanos. Buenos Aires, Argentina.}
    \address[CIMA]{CONICET -- Universidad de Buenos Aires. Centro de Investigaciones del Mar y la Atmósfera (CIMA). Buenos Aires, Argentina.}
    \address[CNRS]{CNRS -- IRD -- CONICET -- UBA. Instituto Franco-Argentino para el Estudio del Clima y sus Impactos (IRL 3351 IFAECI). Buenos Aires, Argentina.}
    \address[SMN]{Servicio Meteorológico Nacional de Argentina.}
    \address[CONICET]{CONICET (Consejo Nacional de Investigaciones Científicas y Técnicas).}
    \address[INPE]{National Institute for Space Research, Brazil, Center for Weather Forecasting and Climate Studies.}
    \address[NCAR]{National Center for Atmospheric Research, Boulder, Colorado.}
    \address[Illinois]{Department of Atmospheric Sciences, University of Illinois Urbana--Champaign, Urbana, Illinois.}
      \cortext[1]{Corresponding Author}

  \begin{abstract}
  In this paper, we evaluate the impact of assimilating high-resolution surface networks and satellite observations using the WRF-GSI-LETKF over central and north eastern Argentina where the surface and upper air observing networks are relatively coarse. We conducted a case study corresponding to a huge mesoscale convective system (MCS) that developed during November 22, 2018. The accumulated precipitation associated with this MCS was quite high, exceeding 200 mm over northern Argentina and Paraguay. The MCS developed during the Intense Observing Period (IOP) of the RELAMPAGO field campaign. We used the GSI-4DLETKF data assimilation package to produce analyses assimilating observations every hour with 10-km horizontal grid spacing and a 60-member multiphysics ensemble. We conducted four assimilation experiments using different sets of observations: CONV, consisting of conventional observations from NCEP's prepBUFR files; AWS combining CONV and dense automatic surface weather station networks, SATWND, combining AWS with satellite-derived winds and RAD, including SATWND; and satellite radiances from different microwave and infrared sensors. We found that the assimilation of observations with high temporal and spatial frequency generate an important impact on the PBL, primarily on the precipitable water content, that leads to the development of deep convection and heavy precipitation closer to the observed in this case study. The assimilation of radiance observations produces a better development of the convection mainly during the mature state of the MCS leading to an increase in the accumulated precipitation. We also ran ensemble forecasts initialized from each experiment and evaluated their skill to predict precipitation. We found that the hourly assimilation of the observations in AWS, SATWND, and RAD helped to improve the precipitation forecast.
  \end{abstract}
   \begin{keyword} Regional Data Assimilation, Surface Observations, Satellite Observations\end{keyword}
 \end{frontmatter}

@@

Severe weather events cause significant human and economic losses around the world. A large number of these phenomena are associated with the occurrence of deep moist convection, including tornadoes, intense wind gusts, extreme precipitation in short time periods, large hail, and lightning.
Southern South America has one of the highest frequencies in the world of favorable conditions for high-impact meteorological events (Brooks et al., 2003) and large hail events (Cecil and Blankenship, 2012), particularly during austral spring and summer.
This is also confirmed by observational evidence and high impact weather reports (Matsudo et al., 2015; Rasmussen et al., 2014). Recently, the RELAMPAGO-CACTI field campaign (Nesbitt et al., 2021) has been conducted to investigate the mechanisms for convective initiation and the occurrence of high-impact weather events associated with deep convection in central Argentina.

Forecasting mesoscale meteorological phenomena and particularly deep moist convection is a scientific and technological challenge due to its limited predictability and the difficulties in diagnosing the state of the atmosphere at small spatial and short temporal scales (for example from 1 to 10 kilometers and on the order of minutes). Mesoscale data assimilation (DA) is an approach that can provide appropriate initial conditions for high-resolution numerical forecasts (Sun et al., 2014) and thus has received increasing attention in the last decades.

For DA methods to be successful, observing networks with sufficient temporal and spatial resolution capable of capturing mesoscale variability should be used.

In that regard, several authors investigated the impact of assimilating surface weather data (e.g.~Wheatley and Stensrud (2010), Ha and Snyder (2014), Chang et al. (2017), Bae and Min (2022), Banos et al. (2021), Maejima et al. (2019), and Chen et al. (2016)) using different assimilation methodologies. Most of these studies reported the beneficial impacts of assimilating temperature and dew point observations upon the planetary boundary layer structure and the location and timing of precipitating systems. Sobash and Stensrud (2015) showed using a mesoscale DA system, that the positive impact upon convection initiation and the short range precipitation forecast is achieved if data is assimilated frequently (in the order of minutes, rather than in the order of hours). More recently, Gasperoni et al. (2018) evaluated the impact of assimilating observations produced by private weather station networks which are not incorporated in the operational analysis. They found a positive effect of these observations upon the initiation of deep moist convection. This result is particularly important for data sparse regions such as Southern South America, where operational networks are not dense enough to capture mesoscale details.

The impact of other types of high spatial and temporal resolution observations, such as atmospheric motion vectors (AMVs), has also been investigated in the context of limited-area mesoscale DA. Many studies have focused on the impact of these observations on the prediction of tropical storms (e.g., Wu et al. (2014), Cherubini et al. (2006), and Sawada et al. (2019), among many others). Most of these studies reported an overall positive impact of the assimilation of AMVs for this type of storm. However, some works indicated mixed impacts (e.g.~Sawada et al. (2019) reported an improvement in the forecast of the track of the storm but a degradation in the forecast intensity). As stated in J. Zhao et al. (2021a) and J. Zhao et al. (2021b), the impact of assimilating these data on high impact weather events associated with mid-latitude deep convection over land has received relatively less attention. J. Zhao et al. (2021a) and J. Zhao et al. (2021b) assimilated GOES-16 AMVs into a storm-scale three-dimensional variational DA system during three high impact weather events. They reported positive impacts of AMVs on the characterization of the storm environment and improved short range precipitation forecasts. Otsuka et al. (2015) and Mallick and Jones (2020) found a slight improvement in the short-range precipitation forecast due to the storm-scale assimilation of high frequency AMVs.

While the assimilation of radiance observations into global models is well established (Eyre et al., 2020), the direct assimilation of radiance data into regional models, however, still remains a challenge due to the sparse data coverage, bias correction, and the relatively low model tops used for this application. Bao et al. (2015) studied the impact of assimilating microwave and infrared radiance data on temperature and humidity forecasts over the western USA and found a reduction in the temperature bias at low and mid-levels as a result of the microwave observations but an opposite effect for infrared data. More recently, Zhu et al. (2019) studied the impact of assimilating satellite radiance data within a frequently updated regional system and showed an improvement for all variables, in particular for relative humidity at upper levels. Wang and Randriamampianina (2021) studied the impact of assimilating radiances in the high-resolution Copernicus European Regional Reanalysis. They reported that satellite radiance observations had a neutral impact on the analyses of geopotential height in the lower troposphere, while a slightly negative impact on the upper troposphere and the stratosphere. They also observed similar results for 3-h forecasts initialized from the analysis but a positive impact on 12 and 24 -h forecasts. Given these mixed results, there is still room to analyze the utility of assimilating radiance observations in a limited-area DA system over land. Moreover, to the best of our knowledge, there are no studies related to the direct assimilation of radiance observations over South America.

In particular, in South America, the relatively scarcity of conventional observations such as radiosondes increases the potential impact of the observation sources previously discussed. Previous work has shown promising results of mesoscale DA in South America using some of the above mentioned data sources (e.g.~Dillon et al., 2016, 2021; Goncalves de Goncalves et al., 2015). In particular Dillon et al. (2021) assimilated high resolution surface weather station networks, GOES-16 AMVs, and satellite temperature and moisture retrievals with promising results. However, no work has been conducted yet over this region to investigate the potential contribution of the datasets discussed above.
The main objective of this work is to contribute to the quantification and comparison of the impact of high resolution surface weather stations, AMVs, and clear-sky satellite radiances, into a mesoscale, frequently-updated ensemble-based DA system. In particular, we will focus on the impact in the context of mid-latitude mesoscale convective system events. Another particular goal of this paper is to investigate the impact of these data sources in a region where the conventional observation network is rather sparse and where the potential contributions of these observing systems is larger.

To reach this goal, we conduct several DA experiments for a case study of a large Mesoscale Convective System (MCS) that developed over Southern South America during Nov 22-23, 2018 during the intense observation period (IOP) of the RELAMPAGO field campaign.

@@

\hypertarget{case-study}{%
\subsection{Case Study}\label{case-study}}

On Nov 22, 2018 a cold front crossed the center of Argentina triggering isolated convective cells that rapidly grew upscale into an exceptionally large MCS. To the north of the region, a warm front contributed to the development of isolated multicells that ultimately grew and merged with the MCS.
The MCS traveled approximately 2500 km from south to north, dissipating over Paraguay and Southern Brazil after 42 hours.

@@

The model simulations for the case study are performed using version 3.9.1 of the non-hydrostatic Advanced Research version of the Weather Research and Forecasting (WRF-ARW, Skamarock et al. (2008)) model.
The horizontal grid spacing is 10 km (150 x 200 grid points) in the horizontal and 37 levels in the vertical with the top of the model at 50 hPa.
The initial and boundary conditions are provided by the Global Forecast System (GFS) analysis (0.25\(^{\circ}\) horizontal grid spacing and 6-hour temporal resolution; National Centers for Environmental Prediction, National Weather Service, NOAA, U.S. Department of Commerce (2015)).
The domain covers the area indicated in Figure \ref{fig:dominio} to capture the development of the MCS during the simulated period.

The analyses are generated using the LETKF implementation (V1.3, Hunt et al. (2007)) part of the Gridpoint Statistical Interpolation analysis system (GSI V3.8; Shao et al. (2016)).
A rapid update cycle approach is implemented with hourly analysis and a centered assimilation window, meaning that all the observations within \(\pm\) 30 minutes of the analysis time are assimilated.
Observations are assimilated in a 4D approach by comparing them with the corresponding first guess state at 10-minute intervals.
For radiance observations, the Community Radiative Transfer Model version 2.3 (CRTM; Han et al. (2006)) is used as an observation operator to calculate model-simulated brightness temperatures.

We use a 60-member ensemble where the ensemble mean at the beginning of the DA cycle is initialized using the GFS deterministic analysis with random perturbations to generate the initial ensemble perturbations. The perturbations are generated as scaled differences between two random atmospheric states obtained from the Climate Forecast System Reanalysis (CFSR) data with 0.5\(^{\circ}\) horizontal grid spacing with a smooth time evolution as in Necker et al. (2020) and Maldonado et al. (2021). In this way, we preserved the nearly hydrostatic and geostrophic equilibrium of larger scales. This method helps to prevent an underestimation of the ensemble spread (Ouaraini et al., 2015), and the random perturbations are also applied at the boundaries to maintain proper levels of ensemble spread within the domain.

In addition to random perturbations at the lateral boundaries, a multi-physics scheme is used to better represent the uncertainty in model formulation within the DA system. We use 9 different model configurations consisting of the combination of 3 moist convection schemes (Kain--Fritsch (Kain, 2004), Grell--Freitas (Grell and Freitas, 2013), and Betts--Miller--Janjic (Janjić, 1994)) and 3 planetary boundary layer schemes (Yonsei University Scheme (Hong, Noh, et al., 2006), Mellor--Yamada--Janjic Scheme (Janjić, 1994), and Mellor--Yamada Nakanishi Niino (Nakanishi and Niino, 2009)). All ensemble members use the same land-surface model (Noah-MP, Chen and Dudhia (2001)), microphysics (WRF single-moment 6--class scheme (Hong, Kim, et al., 2006)), and radiation processes (RRTMG shortwave and longwave scheme (Iacono et al., 2008)) parameterizations.

To reduce the effect of spurious correlations in the estimation of error covariances, we use a horizontal localization radius of 180 km and a vertical localization radius of 0.4 (in log pressure coordinates) as in Dillon et al. (2021) for all types of observations.
A relaxation-to-prior inflation (Whitaker and Hamill, 2012) is applied with an inflation parameter \(\alpha=0.9\) to mitigate the impact of sampling errors and to consider model errors not accounted for by the multi-model ensemble approach.

\begin{figure}
\includegraphics[width=1\linewidth]{../figures/dominio-1} \caption{a) The domain used for the simulations (black box), the inner domain used for the experiment comparison (red box), the region shown in b) (light blue box), and the locations of Automatic Weather Stations (AWS, green squares) and Conventional Surface Weather Stations (CSWS, orange triangles). b) Locations of radiosonde launches during RELAMPAGO. Green dots correspond to radiosondes launched during IOP 7, orange triangles are radiosondes launched during IOP 8, and purple squares are radiosondes launched outside the IOP missions. The topography in meters is also shown (shaded).}\label{fig:dominio}
\end{figure}

@@

The conventional observations used are part of the Global Data Assimilation System (GDAS) data stream. We assimilated conventional observations included in the Binary Universal Form for Representation of Meteorological Data (PREPBUFR) files generated at the National Centers for Environmental Prediction (NCEP). These consist of surface observations from 117 Conventional Surface Weather Stations (CSWS), ships, and upper-air observations from 13 radiosondes sites and aircraft. The orange triangles in Figure \ref{fig:dominio}a indicate the location of the surface stations included in this experiment. The frequency of these observations varied between 1 hour for surface stations and 12/24 hours for radiosondes. Wind surface observations over oceans (ASCATW) come from scatterometers and are also included in the PREPBUFR files.

@@

We also assimilate data from 866 Automatic Weather Stations (AWS) that are part of 17 public and private surface networks over Southern South America. The dataset used in this study has been obtained from the RELAMPAGO Data Set repository (Garcia et al., 2019). These stations are indicated as green squares in Figure \ref{fig:dominio}a. They have higher spatial coverage than the CSWS and a sampling frequency of 10 minutes in most cases. All stations measure temperature, but only 395 stations provide humidity, 422 provide pressure, and 605 provide wind information.
Observation errors used to assimilate these observations are the same as for the CSWS (see Table \ref{tab:table-obs}).

\hypertarget{satellite-derived-winds}{%
\subsubsection{Satellite derived winds}\label{satellite-derived-winds}}

>>>>

\documentclass[preprint, 3p, authoryear,review, 12pt]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%

\usepackage[hyphens]{url}

@@

\usepackage{lineno} % add
  \linenumbers % turns line numbering on

@@

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[]{natbib}
\bibliographystyle{plainnat}

\usepackage{graphicx}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Hourly Assimilation of Different Sources of Observations Including Satellite Radiances in a Mesoscale Convective System Case During RELAMPAGO campaign},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}

@@

\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

  \title{Hourly Assimilation of Different Sources of Observations Including Satellite Radiances in a Mesoscale Convective System Case During RELAMPAGO campaign}
    \author[UBA,CIMA,CNRS]{Paola Belén Corrales%
  %
  \fnref{1}}
   \ead{paola.corrales@cima.fcen.uba.ar} 
    \author[UBA,CIMA,CNRS]{V. Galligani}

@@

      \affiliation[UBA]{Universidad de Buenos Aires, Facultad de Ciencias Exactas y Naturales, Departamento de Ciencias de la Atmosfera y los Oceanos. Buenos Aires, Argentina.}
    \affiliation[CIMA]{CONICET -- Universidad de Buenos Aires. Centro de Investigaciones del Mar y la Atmosfera (CIMA). Buenos Aires, Argentina.}
    \affiliation[CNRS]{CNRS -- IRD -- CONICET -- UBA. Instituto Franco-Argentino para el Estudio del Clima y sus Impactos (IRL 3351 IFAECI). Buenos Aires, Argentina.}
    \affiliation[SMN]{Servicio Meteorologico Nacional de Argentina.}
    \affiliation[CONICET]{CONICET (Consejo Nacional de Investigaciones Cientificas y Tecnicas).}
    \affiliation[INPE]{National Institute for Space Research, Brazil, Center for Weather Forecasting and Climate Studies.}
    \affiliation[NCAR]{National Center for Atmospheric Research, Boulder, Colorado.}
    \affiliation[Illinois]{Department of Atmospheric Sciences, University of Illinois Urbana--Champaign, Urbana, Illinois.}
    \cortext[cor1]{Corresponding author}
    \fntext[1]{Corresponding Author}

  \begin{abstract}
  This paper evaluates the impact of assimilating high-resolution surface networks and satellite observations using the WRF-GSI-LETKF over central and north eastern Argentina where the surface and upper air observing networks are relatively coarse. A case study corresponding to a huge mesoscale convective system (MCS) that developed during November 22, 2018 was used. The accumulated precipitation associated with this MCS was quite high, exceeding 200 mm over northern Argentina and Paraguay. The MCS developed during the Intense Observing Period (IOP) of the Remote sensing of Electrification, Lightning, And Mesoscale/microscale Processes with Adaptive Ground Observations (RELAMPAGO) field campaign. The GSI-4DLETKF data assimilation package is used to produce analyses by assimilating observations every hour with 10-km horizontal grid spacing and a 60-member multiphysics ensemble. Four assimilation experiments are conducted using different sets of observations: CONV, consisting of conventional observations from NCEP's prepBUFR files; AWS, combining CONV and dense automatic surface weather station networks (AWS), SATWND, combining AWS with satellite-derived winds, and RAD, including SATWND; and satellite radiances from different microwave and infrared sensors. The assimilation of observations with high temporal and spatial frequency generates an important impact on the PBL, primarily on the precipitable water content, that leads to the development of deep convection and heavy precipitation closer to the observed in this case study. The assimilation of radiance observations produces a better development of the convection mainly during the mature state of the MCS leading to an increase in the accumulated precipitation. Ensemble forecasts initialized from each experiment were also simulated to evaluate their skill to predict precipitation. The hourly assimilation of the observations in AWS, SATWND, and RAD helped to improve the precipitation forecast.
  \end{abstract}
    \begin{keyword}
    Regional Data Assimilation, Surface Observations, Satellite Observations \sep 
    Regional Data Assimilation, Surface Observations, Satellite Observations
  \end{keyword}

 \end{frontmatter}

@@

Severe weather events cause significant human and economic losses around the world. A large number of these phenomena are associated with the occurrence of deep moist convection, including tornadoes, intense wind gusts, extreme precipitation in short time periods, large hail, and lightning.
Southern South America has one of the highest frequencies in the world of favorable conditions for high-impact meteorological events \citep{brooks2003} and large hail events \citep{cecil2012}, particularly during austral spring and summer.
This is also confirmed by observational evidence and high impact weather reports \citep{matsudo2015, rasmussen2014}. Recently, the Remote sensing of Electrification, Lightning, And Mesoscale/microscale Processes with Adaptive Ground Observations (RELAMPAGO) field campaign \citep{nesbitt2021} has been conducted to investigate the mechanisms for convective initiation and the occurrence of high-impact weather events associated with deep convection in central Argentina.

Forecasting mesoscale meteorological phenomena and particularly deep moist convection is a scientific and technological challenge due to its limited predictability and the difficulties in diagnosing the state of the atmosphere at small spatial and short temporal scales (for example from 1 to 10 kilometers and on the order of minutes). Mesoscale data assimilation (DA) is an approach that can provide appropriate initial conditions for high-resolution numerical forecasts \citep{sun2014} and thus has received increasing attention in the last decades.

For DA methods to be successful, observing networks with sufficient temporal and spatial resolution capable of capturing mesoscale variability should be used \citep{gustafsson2018}. Assimilating information on temperature, moisture, and wind in the planetary boundary layer (PBL) improves mesoscale model initialization, and several authors have reported the resultant beneficial impacts on the PBL structure and the location and timing of precipitating systems (e.g. \citet{wheatley2010}, \citet{ha2014}, \citet{chang2017}, \citet{bae2022}, \citet{banos2021}, \citet{maejima2019}, and \citet{chen2016}).

Particularly relevant for regional mesoscale DA systems in the region of interest is that South America is characterized by a limited number of conventional observations (i.e., radiosondes, surface weather stations) and operational networks that are not dense enough to capture mesoscale details. In this context, analyzing the potential impact of non-conventional sources of observations is essential to improve mesoscale numerical weather prediction (NWP) over South America using DA. There have been only a few published efforts on regional mesoscale DA, but they have all shown promising results \citep[e.g.][]{dillon2016, dillon2021, goncalvesdegoncalves2015}. In particular, \citet{dillon2021} assimilated high resolution surface weather station networks, GOES-16 atmospheric motion vectors (AMVs), and satellite temperature and moisture retrievals over central Argentina with positive impacts. Similar to \citet{gasperoni2018}, \citet{dillon2021} included private weather station networks which are not incorporated in the operational analysis. However, the impact of different observation types on the analysis quality has not been addressed.

The impact of non-conventional high spatial and temporal resolution observations, such as AMVs, has been investigated in the context of regional mesoscale DA. Many studies have focused on the impact of these observations on the prediction of tropical storms (e.g., \citet{wu2014}, \citet{cherubini2006}, and \citet{sawada2019}, and many others). Most of these studies reported an overall positive impact of the assimilation of AMVs for this type of storm. However, some works indicated mixed impacts (e.g. \citet{sawada2019} reported an improvement in the forecast of the track of the storm but a degradation in the forecast intensity). As stated in \citet{zhao2021, zhao2021a}, the impact of assimilating these data on high impact weather events associated with mid-latitude deep convection over land has received relatively less attention. \citet{zhao2021, zhao2021a} assimilated GOES-16 AMVs into a storm-scale three-dimensional variational DA system during three high impact weather events. They reported positive impacts of AMVs on the characterization of the storm environment and improved short range precipitation forecasts. \citet{otsuka2015} and \citet{mallick2020} found a slight improvement in the short-range precipitation forecast due to the storm-scale assimilation of high frequency AMVs.

While the assimilation of radiance observations into global models is well established \citep{eyre2020}, the direct assimilation of radiance data into regional models, however, still remains a challenge due to the sparse data coverage (in the case of polar-orbiting satellite observations), bias correction, and the relatively low model tops used for this application. \citet{bao2015} studied the impact of assimilating cloud-cleared microwave and infrared radiance data polar orbiting instruments on temperature and humidity forecasts over the western USA and found a reduction in the temperature bias at low and mid-levels as a result of the microwave observations but an opposite effect for infrared data. More recently, \citet{zhu2019} studied the impact of assimilating clear sky polar orbiting satellite radiance data within a frequently updated regional system and showed an improvement for all variables, in particular for relative humidity at upper levels. \citet{wang2021} studied the impact of assimilating clear sky radiances in the high-resolution Copernicus European Regional Reanalysis. They reported that satellite radiance observations had a neutral impact on the analyses of geopotential height in the lower troposphere, while a slightly negative impact on the upper troposphere and the stratosphere. They also observed similar results for 3-h forecasts initialized from the analysis but a positive impact on 12 and 24 -h forecasts. Given these mixed results, there is still room to analyze the utility of assimilating radiance observations in a limited-area DA system over land. Moreover, to the best of our knowledge, there are no studies related to the direct assimilation of radiance observations over South America.

The main objective of this work is thus to contribute to the quantification and comparison of the impact of high resolution automatic weather stations, AMVs, and clear-sky satellite radiances, into a mesoscale, frequently-updated ensemble-based regional DA system. This is particularly important in the efforts to improve mesoscale numerical weather prediction (NWP) over South America where the conventional observation network is rather sparse and other sources of information could potentially fill certain gaps. In particular, this paper focuses on the impact in the context of a mid-latitude mesoscale convective system. To reach this goal, several DA experiments are conducted for a case study of a large Mesoscale Convective System (MCS) that developed over Southern South America during Nov 22-23, 2018 during the intense observation period (IOP) of the RELAMPAGO field campaign.

@@

\hypertarget{case-overview}{%
\subsection{Case overview}\label{case-overview}}

Previously to the development of this case study, the center and north of Argentina was immersed in a warm and humid air mass with high values of convective available potential energy (CAPE), as shown by ERA 5 Reanalysis \citep{era5pressure} in Figure \ref{fig:case}a. On Nov 22, 2018 a cold front crossed the center of Argentina (Figure \ref{fig:case}b). This cold front triggered isolated convective cells that rapidly grew upscale into an exceptionally large MCS (Figure \ref{fig:case}d,e). During that day several surface stations reported lightning, strong wind gusts, and heavy rain. To the north of the region, a warm and humid environment contributed to the development of isolated convection that ultimately grew and merged with the MCS (Figure \ref{fig:case}f).
The MCS traveled approximately 2500 km from south to north, dissipating over Paraguay and Southern Brazil after 42 hours.

\begin{figure*}

{\centering \includegraphics{../figures/case-1}

\caption{ERA5 Reanalysis of sea level pressure (hPa, black contours), 1000-500 hPa thickness (red dashed contours) and convective available potential energy (shaded) and GOES-16 channel 13 brightness temperature for a,d) 00 and b,e) 12 UTC Nov 22 and c,f) 00 UTC Nov 23.}\label{fig:case}
\end{figure*}

@@

The forecast model uses the non-hydrostatic Advanced Research version of Weather Research and Forecasting (WRF-ARW V3.9.1, \citet{skamarock2008}).
The horizontal grid spacing is 10 km (150 x 200 grid points) in the horizontal and 37 levels in the vertical with the top of the model at 50 hPa.
The initial and boundary conditions are provided by the Global Forecast System (GFS) analysis (0.25\(^{\circ}\) horizontal grid spacing and 6-hour temporal resolution; \citet{cisl_rda_ds084.1}). In this case, a single nesting approach is used since the resolution gap between the driving model and the regional model is not too large (0.25\(^{\circ}\) or 25 km approximately to 10 km). This approach is also based on recent studies which suggest that using multiple nested domains does not necessarily lead to improved precipitation forecasts in regional domains, particularly in areas of complex terrain (e.g. \citet{liang2019}, \citet{beck2004}). The domain covers the area indicated in Figure \ref{fig:dominio} to capture the development of the MCS during the simulated period.

The analyses are generated using the LETKF implementation (V1.3, \citet{hunt2007}) of the Gridpoint Statistical Interpolation analysis system (GSI V3.8; \citet{shao2016}).
A rapid update cycle approach is implemented with hourly analysis and a centered assimilation window, meaning that all the observations within \(\pm\) 30 minutes of the analysis time are assimilated.
Observations are assimilated in a 4D approach by comparing them with the corresponding first guess state at 10-minute intervals.
For radiance observations, the Community Radiative Transfer Model version 2.3 (CRTM; \citet{han2006}) is used as an observation operator to calculate model-simulated brightness temperatures.

A 60-member ensemble is used where the initial ensemble mean and the mean boundary conditions are taken from the GFS deterministic analysis. A set of 60 perturbations are randomly generated to perturb the initial state as well as the boundary conditions during the length of the experiment. Perturbing the boundary conditions helps to reduce the impact of errors in the driving global model and helps to keep a larger ensemble spread throughout the domain and during the length of the experiment \citep{ouaraini2015}. The perturbations are generated as scaled differences between two random atmospheric states obtained from the Climate Forecast System Reanalysis (CFSR) data with 0.5\(^{\circ}\) horizontal grid spacing with a smooth time evolution as in \citet{necker2020} and \citet{maldonado2021}. In this way, the nearly hydrostatic and geostrophic equilibrium of larger scales is preserved. The random perturbations used are the same across experiments to ensure that the differences between experiments are only related to changes in the number and type of assimilated observations.

A multi-physics scheme is used to better represent the uncertainty in the model formulation within the DA system. 9 different model configurations are generated consisting of the combination of 3 moist convection schemes (Kain--Fritsch \citep{kain2004}, Grell--Freitas \citep{grell2013}, and Betts--Miller--Janjic \citep{janjic1994}) and 3 planetary boundary layer schemes (Yonsei University Scheme \citep{hong2006}, Mellor--Yamada--Janjic Scheme \citep{janjic1994}, and Mellor--Yamada Nakanishi Niino \citep{nakanishi2009}). The distribution of these schemes among the 60 ensemble members is outlined in Table \ref{tab:miembros-desc}. The multi-physics approach is also introduced in order to represent the uncertainty associated with the more relevant physical processes that are not resolved by the model. All ensemble members use the same land-surface model (Noah-MP, \citet{chen2001}), microphysics (WRF single-moment 6--class scheme \citep{hong2006a}), and radiation processes (RRTMG shortwave and longwave scheme \citep{iacono2008}) parameterizations.

\caption{\label{tab:miembros-desc}Generation of the 60-member multi-physics ensemble as a combination of Cumulus and PBL parameterizations.}
\centering
\fontsize{6}{8}\selectfont
\begin{tabular}[t]{c>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{PBL} \\
\cmidrule(l{3pt}r{3pt}){2-4}
Cumulus & MYJ & MYNN2 & YSU\\
\midrule
BMJ & 5, 14, 23, 32, 41, 50, 59 & 8, 17, 26, 35, 44, 53 & 2, 11, 20, 29, 38, 47, 56\\
GF & 6, 15, 24, 33, 42, 51, 60 & 9, 18, 27, 36, 45, 54 & 3, 12, 21, 30, 39, 48, 57\\
KF & 4, 13, 22, 31, 40, 49, 58 & 7, 16, 25, 34, 43, 52 & 1, 10, 19, 28, 37, 46, 55\\
\bottomrule
\end{tabular}
\end{table}

To reduce the effect of spurious correlations in the estimation of error covariances, a horizontal localization radius of 180 km and a vertical localization radius of 0.4 (in log pressure coordinates) is used as in \citet{dillon2021} for all types of observations.
A relaxation-to-prior spread inflation \citep{whitaker2012} is applied with an inflation parameter \(\alpha=0.9\) following \citet{maldonado2020} to mitigate the impact of sampling errors and to consider model errors not accounted for by the multi-model ensemble approach.

\begin{figure}
\includegraphics[width=0.98\linewidth]{../figures/dominio-1} \caption{a) The domain used for the simulations (black box), the inner domain used for the experiment comparison (red box), the region shown in b) (light blue box), and the locations of Automatic Weather Stations (AWS, green squares) and Conventional Surface Weather Stations (CSWS, orange triangles). b) Locations of radiosonde launches during RELAMPAGO. Green dots correspond to radiosondes launched during IOP 7, orange triangles are radiosondes launched during IOP 8, and purple squares are radiosondes launched outside the IOP missions. The topography in meters is also shown (shaded).}\label{fig:dominio}
\end{figure}

@@

The conventional observations used are part of the Global Data Assimilation System (GDAS) data stream. Conventional observations included in the Binary Universal Form for Representation of Meteorological Data (PREPBUFR) files generated at the National Centers for Environmental Prediction (NCEP) are assimilated. These consist of surface observations from 117 Conventional Surface Weather Stations (CSWS), ships, and upper-air observations from 13 radiosondes sites and aircraft. The orange triangles in Figure \ref{fig:dominio}a indicate the location of the surface stations included in this experiment. The frequency of these observations varied between 1 hour for surface stations and 12/24 hours for radiosondes. Wind surface observations over oceans (ASCATW) come from scatterometers and are also included in the PREPBUFR files.

@@

Data from 866 Automatic Weather Stations (AWS) that are part of 17 public and private surface networks over Southern South America are also assimilated. The dataset used in this study has been obtained from the RELAMPAGO Data Set repository \citep{garcia2019}. These stations are indicated as green squares in Figure \ref{fig:dominio}a. They have higher spatial coverage than the CSWS and a sampling frequency of 10 minutes in most cases. All stations measure temperature, but only 395 stations provide humidity, 422 provide pressure, and 605 provide wind information.
Observation errors used to assimilate these observations are the same as for the CSWS (see Table \ref{tab:table-obs}).

\hypertarget{satellite-derived-winds}{%
\subsubsection{Satellite-derived winds}\label{satellite-derived-winds}}
